Multisensor Architecture for an Intersection Management System

### 2015-06-10 ch2-mdf_ims.tex
Added content to the last section of chapter 2

>>>>

Cameras are a wide used sensor for surveillance and monitoring applications because they provide a lot of information for scene understanding, but the transmitting and processing of such information requires high computational resources. For this reason low resolution cameras and low frame rates configurations are commonly deployed. On the other hand, range sensor, such as lasers and lidars, have been recently included in Intersection management systems, as unique sensors or with cameras too. One of the benefits of range sensors is that because of information volume is less than provided by cameras, its processing requirements are lower. Using both cameras and range sensors for intersection management systems makes it possible to take advantages of each type of sensor, and obtain a better representation of the environment.
